---
title: "Model 3"
author: "Idzhar A. Lakibul"
date: "`r Sys.Date()`"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#K-means Clustering
```{r, message=FALSE}
library(dplyr)
library(ggplot2)
library(stringr)
library(gridExtra)
library(factoextra)
library(tidyverse)
library(cluster)
library(readr)
library(mclust)
library(tidyr)
library(tibble)
library(purrr)
library(utils)
```

```{r, message=FALSE}
radiomics_completedata <- read_csv("C:/STAT 371/Final Project/radiomics_completedata.csv")
 View(radiomics_completedata)
 Rad<-radiomics_completedata
```

#To remove any missing value that might be present in the data, type this:

```{r, message=FALSE}
Rad <- na.omit(Rad)
```

#we start by scaling/standardizing the data

```{r, message=FALSE}
Rad <- scale(Rad[,-c(1,2)])
head(Rad)
```
#function to compute total within-cluster sum of square 
```{r, message=FALSE}
set.seed(123)
wss <- function(k) {
  kmeans(Rad, k, nstart = 10 )$tot.withinss
}
```
# Compute and plot wss for k = 1 to k = 20
```{r, message=FALSE}
k.values <- 1:20
```
# extract wss for 2-15 clusters
```{r, message=FALSE}
wss_values <- map_dbl(k.values, wss)
plot(k.values, wss_values,
     type="b", pch = 19, frame = FALSE, 
     xlab="Number of clusters K",
     ylab="Total within-clusters sum of squares")
```

#or use thE silhouette
```{r, message=FALSE}
fviz_nbclust(Rad, kmeans, method = "silhouette")
```
# compute gap statistic
```{r, message=FALSE}
set.seed(123)
gap_stat <- clusGap(Rad, FUN = kmeans, nstart = 25,
                    K.max = 10, B = 50)
```
# Print the result
```{r, message=FALSE}
print(gap_stat, method = "firstmax")
fviz_gap_stat(gap_stat)
```
# Compute k-means clustering with k = 2
```{r, message=FALSE}
set.seed(123)
final <- kmeans(Rad, 2, nstart = 25)
print(final)
```
#final data
```{r, message=FALSE}
fviz_cluster(final, data = Rad)

```

#Hieralchical method

```{r, message=FALSE}
d <- dist(Rad, method = "euclidean")
```

# methods to assess

```{r, message=FALSE}
set.seed(123)
```

```{r, message=FALSE}
m <- c( "average", "single", "complete", "ward")
names(m) <- c( "average", "single", "complete", "ward")
```

#function to compute coefficient

```{r, message=FALSE}
ac <- function(x) {
  agnes(Rad, method = x)$ac
}
```

#Get agglomerative coefficient for each linkage method

```{r, message=FALSE}
purrr::map_dbl(m, ac)
```

#compute divisive hierarchical clustering

```{r, message=FALSE}
diana <- diana(Rad)
diana$dc
```

#Plot cluster results

```{r, message=FALSE}
p_EM <- fviz_nbclust(Rad, FUN = hcut, method = "wss", 
                   k.max = 10) +
  ggtitle("(A) Elbow method")
```

```{r, message=FALSE}
p_SM <- fviz_nbclust(Rad, FUN = hcut, method = "silhouette", 
                   k.max = 10) +
  ggtitle("(B) Silhouette method")
```

```{r, message=FALSE}
p_GS <- fviz_nbclust(Rad, FUN = hcut, method = "gap_stat", 
                   k.max = 10) +
  ggtitle("(C) Gap statistic")
```

```{r, message=FALSE}
gridExtra::grid.arrange(p_EM, p_SM, p_GS, nrow = 1)
```

#Dendorgram for the Radiomic dataset

```{r, message=FALSE}
hc_final <- hclust(d, method = "ward.D2" )
```

```{r, message=FALSE}
dend_plot <- fviz_dend(hc_final)
```

```{r, message=FALSE}
dend_data <- attr(dend_plot, "dendrogram")
```

```{r, message=FALSE}
dend_cuts <- cut(dend_data, h = 70.5)
```

```{r, message=FALSE}
fviz_dend(dend_cuts$lower[[1]])
```

#Number of members in each cluster

```{r, message=FALSE}
hc_final <- hclust(d, method = "ward.D2" )
```

```{r, message=FALSE}
sub_grp <- cutree(hc_final, k = 2)
```

```{r, message=FALSE}
table(sub_grp)
```

# Plot full dendogram

```{r, message=FALSE}
fviz_dend(
  hc_final,
  k = 2,
  horiz = TRUE,
  rect = TRUE,
  rect_fill = TRUE,
  rect_border = "jco",
  k_colors = "jco",
  cex = 0.1)
```


# Model Based

# Apply GMM model with 3 components


```{r, message=FALSE}
Rad_mbc <- Mclust(Rad, G = 3)
```

# Plot results

```{r, message=FALSE}
plot(Rad_mbc, what = "density")
plot(Rad_mbc, what = "uncertainty")
```

# Observations with high uncertainty

```{r, message=FALSE}
sort(Rad_mbc$uncertainty, decreasing = TRUE) %>% head()
summary(Rad_mbc)
```

```{r, message=FALSE}
Rad_optimal_mbc <- Mclust(Rad)
summary(Rad_optimal_mbc)
```

# Plot

```{r, message=FALSE}
legend_args <- list(x = "bottomright", ncol = 5)
plot(Rad_optimal_mbc, what = 'BIC', legendArgs = legend_args)
plot(Rad_optimal_mbc, what = 'classification')
plot(Rad_optimal_mbc, what = 'uncertainty')
```

```{r, message=FALSE}
Rad_mc <- Mclust(Rad, 1:20)

summary(Rad_mc)
```

```{r, message=FALSE}
plot(Rad_mc, what = 'BIC', 
     legendArgs = list(x = "bottomright", ncol = 5))
```

```{r, message=FALSE}
probabilities <- Rad_mc$z 
probabilities
```












